\documentclass{article}
\usepackage[a4paper, left=2cm, right=2cm, top=2cm, bottom=2cm,textwidth=17cm,textheight=23cm]{geometry}
\usepackage{xeCJK}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{xcolor}
\setCJKmainfont{標楷體-繁}
\setmainfont{Times New Roman}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\textsf{\thepage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\title{\fontsize{16pt}{16pt}\selectfont Political Theory}
\author{}
\date{}
\begin{document}
\setstretch{1.05}
\maketitle
\fontsize{14pt}{14pt}\selectfont
\begin{flushleft}
Instructor Information
\end{flushleft}
\begin{itemize}
\item Instructor: Dr. Tzu-Chi Hsiao. \\
\item Office: Room 506, Department of Political Science. \\
\item Office hours: 08:20-09:10, Every Wednesday. \\
\item Email: \href{mailto:politics.tchsiao@gmail.com}{politics.tchsiao@gmail.com}. \\
\item Webpage: \href{https://politics-tchsiao.github.io/website/}{https://politics-tchsiao.github.io/website/}. \\
\end{itemize}
Course Information \\
\begin{itemize}
\item Course: Political Theory. \\
\item Credit: 2. \\
\item Hours: 14:20-16:10, Every Thursday. \\
\item Prerequisite: Politics and Comparative Politics. \\
\item Webpage: \href{https://politics-tchsiao.github.io/political\_theory/}{https://politics-tchsiao.github.io/political\_theory/}. \\
\item Course description \\
In this course, we will introduce subset of Political Science. Every conflicts or struggles are based on ideologies, you must learn the origin and solutions of classical ideologies. Last, each students need to find an interest ideology to present their ideas. \\ 
\item Course objectives \\
0. Need to REVISE then. \\
1. To understand the basic concepts of each ideologies. \\
2. To understand the basic concepts of each solutions. \\
3. To understand the basic concepts of each political systems. \\
\end{itemize}
\newpage
\begin{flushleft}
Grading \\
\end{flushleft}
\begin{itemize}
\item Midterm examination: 40\%. \\
\item Presentation: 60\%. \\
\end{itemize}
Textbook \\
\begin{itemize}
\item \textit{Political Theory}, latest edition, written by Dr. Andew Heywood. \\
\end{itemize}
Course Schedule \\
\begin{itemize}
\item Please refer to the \href{https://politics-tchsiao.github.io/political_theory/}{course webpage}. \\
\end{itemize}
\end{document}
